Modern Graph Generators: A Survey

### 2018-09-28 comparison.tex
Added two paragramhs of summary for social networks

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part B)} {
\begin{tabular}{| c | p{2.2cm}| p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline  % ======================  graph databases
\multirow{7}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\
\cline{2-10}
  & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, zipfian &  N-triples & N    \\
\cline{2-10}
  & graphGen & pattern-driven (Cypher schema) & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
\hline
\hline %  ======================   social networks
\multirow{8}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & fixed & social network & N & N & Y & simulation-driven & -- &  -- \\
\cline{2-10}
 & \cite{Yao2011} & fixed & social network & N & N & N & power-law & -- & --  \\
\cline{2-10}
 & LinkBench & fixed & social network & Y & Y & Y & Facebook & -- & -- \\
\cline{2-10}
 & S3G2 & Y & Y  & N &  & Y & Facebook  & CSV, RDF & Y   \\
\cline{2-10}
 & \cite{Sukthankar-SocialInfo2014} & schema-driven & social-network & N & N & Y & power-law & CSV & N   \\
\cline{2-10}
 & LDBC SNB  & Y & Y &   generated &  & Y & Facebook &  CSV, RDF & Y     \\
\cline{2-10}
  & \cite{Nettleton2016} & schema-driven & social network & N & N & Y & power-law & -- & N  \\
%\cline{2-10}
% & SNG  & Y & Y &   N &  & Y & power-law & ? &  ?   \\
%\cline{2-10}
% & Forest Fire  & N & Y   & N &  & N & power-law &  ? & N   \\
\hline
\hline   % ======================   graph analytics
\multirow{3}{*}{\rot{\textbf{Ana.}}}
  & HPC Scalable Graph Analysis & fixed & & Y & N& N& uniform & & N   \\
\cline{2-10}
  & Graphalytics & extracted & social network & Y& N& power law & & & N   \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St.}}}
  & S2Gen & schema-driven & Social Network & Y & N & N & user-defined & RDF & N     \\
\cline{2-10}
  & RSPLab & schema-driven & Agnostic & Y & Y & N & user-defined & RDF & N     \\
%\cline{2-10}
%  & & & & & & & &  &   \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsB}
\end{sidewaystable}

@@

\begin{table}[h]
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               & \textbf{\rot{Analytics}}
               & \textbf{\rot{Steaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{6}{*}{\rot{\textbf{General}}}
  & \cite{barabasi1999emergence} & x & & & & & \\
\cline{2-8}
   & R-MAt    & x & & & & & \\
\cline{2-8}
  & GraphGen  & x & & & & & \\
\cline{2-8}
  & Graph 500 & x & & & & & \\
\cline{2-8}
  & BTER      & x & & & & & \\
\cline{2-8}
  & Darwini   & x & & & & & \\
\hline
\hline %  ======================  Semantic web
\multirow{15}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & x & & & & \\
\cline{2-8}
 & LBBM  & & x & & & & \\
\cline{2-8}
 & UOBM  & & x & & & & \\
\cline{2-8}
 & IIMB & & x & & & & \\
\cline{2-8}
 & BSBM & & x & & & & \\
\cline{2-8}
 & SP$^2$Bench & & x & & & & \\
\cline{2-8}
 & \cite{Duan:2011:AOC:1989323.1989340} & & x & & & & \\
\cline{2-8}
 & DBPSB & & x & & & & \\
\cline{2-8}
 & LODIB & & x & & & & \\
\cline{2-8}
 & SIB & & x & & & & \\
\cline{2-8}
 & Geographica & & x & & & & \\
\cline{2-8}
 & WatDiv & & x & & & & \\
\cline{2-8}
 & RBench & & x & & & & \\
\cline{2-8}
 & LDBC SPB & & x & & & & \\
\cline{2-8}
 & LinkGen & & x & & & & \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & x & & & \\
\cline{2-8}
  & gMark & & & x & & & \\
\cline{2-8}
  & graphGen & & & x & & & \\
\hline
\hline %  ======================   social networks
\multirow{7}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & x & & \\
\cline{2-8}
 & \cite{Yao2011}  & & & & x & & \\
\cline{2-8}
 & LinkBench  & & & & x & & \\
\cline{2-8}
 & S3G2  & & x & x & x & & \\
\cline{2-8}
 & \cite{Sukthankar-SocialInfo2014}  & & & & x & & \\
\cline{2-8}
 & LDBC SNB   & & x & x & x & & \\
\cline{2-8}
  & \cite{Nettleton2016}  & & & & x & & \\
\hline
\hline   % ======================   graph analytics
\multirow{2}{*}{\rot{\textbf{An.}}}
  & HPC Scalable Graph Analysis  & & & & & x & \\
\cline{2-8}
  & Graphalytics & & & & & x & \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St.}}}
  & S2Gen & & & & & & x\\
\cline{2-8}
  & RSPLab & & & & & & x \\
%\cline{2-8}
%  & & & & & & \\
\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

As we can see ... \TODO{Add a summary.} LDBC can be also seen as graph databases
(even tough it is not specific for them, it is clear it was designed for such
technologies).

>>>>

\begin{sidewaystable}
\scriptsize
\centering
\tbl{Key characteristics of the generators (part B)} {
\begin{tabular}{| c | p{2.2cm}| p{2cm} |  p{2.2cm} | l |  l | l | p{3cm} | p{1.4cm} | l | }
 \hline
           &   & \multicolumn{2}{c}{\textbf{Domain}}
               & \multicolumn{2}{|c|}{\textbf{Operations}}
               & \multicolumn{4}{c|}{\textbf{Configuration}}
               \\ \hline
           &  \textbf{Generator}
               & \textbf{Type}
               & \textbf{Target / sample}
               & \textbf{Read}
               & \textbf{Update}
               & \textbf{\rot{Properties}}
               & \textbf{Distributions}
			   & \textbf{Output}
               & \textbf{\rot{Distributed\ }}
               \\ \hline
\hline  % ======================  graph databases
\multirow{7}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\
\cline{2-10}
  & gMark & schema-driven (internal schema) &  user-defined  & generated &  N  & Y & uniform, normal, zipfian &  N-triples & N    \\
\cline{2-10}
  & graphGen & pattern-driven (Cypher schema) & user-defined  & -- & -- & Y & -- &  property graphs & N   \\
\hline
\hline %  ======================   social networks
\multirow{8}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & fixed & social network & N & N & Y & simulation-driven & -- &  -- \\
\cline{2-10}
 & \cite{Yao2011} & fixed & social network & N & N & N & power-law & -- & --  \\
\cline{2-10}
 & LinkBench & fixed & social network & Y & Y & Y & Facebook & -- & -- \\
\cline{2-10}
 & S3G2 & fixed & social network  & N & N  & Y & Facebook  & CSV, RDF & Y   \\
\cline{2-10}
 & \cite{Sukthankar-SocialInfo2014} & schema-driven & social-network & N & N & Y & power-law & CSV & N   \\
\cline{2-10}
 & LDBC SNB  & fixed & social network &  generated & Y  & Y & Facebook &  CSV, RDF & Y     \\
\cline{2-10}
  & \cite{Nettleton2016} & schema-driven & social network & N & N & Y & power-law & -- & N  \\
%\cline{2-10}
% & SNG  & Y & Y &   N &  & Y & power-law & ? &  ?   \\
%\cline{2-10}
% & Forest Fire  & N & Y   & N &  & N & power-law &  ? & N   \\
\hline
\hline   % ======================   graph analytics
\multirow{3}{*}{\rot{\textbf{Ana.}}}
  & HPC Scalable Graph Analysis & fixed & & Y & N& N& uniform & & N   \\
\cline{2-10}
  & Graphalytics & extracted & social network & Y& N& power law & & & N   \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St.}}}
  & S2Gen & schema-driven & Social Network & Y & N & N & user-defined & RDF & N     \\
\cline{2-10}
  & RSPLab & schema-driven & Agnostic & Y & Y & N & user-defined & RDF & N     \\
%\cline{2-10}
%  & & & & & & & &  &   \\
\hline
\end{tabular} }
\label{tab:comparisonCharacteristicsB}
\end{sidewaystable}

@@

\begin{table}[h]
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               & \textbf{\rot{Analytics}}
               & \textbf{\rot{Steaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{6}{*}{\rot{\textbf{General}}}
  & \cite{barabasi1999emergence} & x & & & & & \\
\cline{2-8}
   & R-MAt    & x & & & & & \\
\cline{2-8}
  & GraphGen  & x & & & & & \\
\cline{2-8}
  & Graph 500 & x & & & & & \\
\cline{2-8}
  & BTER      & x & & & & & \\
\cline{2-8}
  & Darwini   & x & & & & & \\
\hline
\hline %  ======================  Semantic web
\multirow{15}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & x & & & & \\
\cline{2-8}
 & LBBM  & & x & & & & \\
\cline{2-8}
 & UOBM  & & x & & & & \\
\cline{2-8}
 & IIMB & & x & & & & \\
\cline{2-8}
 & BSBM & & x & & & & \\
\cline{2-8}
 & SP$^2$Bench & & x & & & & \\
\cline{2-8}
 & \cite{Duan:2011:AOC:1989323.1989340} & & x & & & & \\
\cline{2-8}
 & DBPSB & & x & & & & \\
\cline{2-8}
 & LODIB & & x & & & & \\
\cline{2-8}
 & SIB & & x & & & & \\
\cline{2-8}
 & Geographica & & x & & & & \\
\cline{2-8}
 & WatDiv & & x & & & & \\
\cline{2-8}
 & RBench & & x & & & & \\
\cline{2-8}
 & LDBC SPB & & x & & & & \\
\cline{2-8}
 & LinkGen & & x & & & & \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & x & & & \\
\cline{2-8}
  & gMark & & & x & & & \\
\cline{2-8}
  & graphGen & & & x & & & \\
\hline
\hline %  ======================   social networks
\multirow{7}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & x & & \\
\cline{2-8}
 & \cite{Yao2011}  & & & & x & & \\
\cline{2-8}
 & LinkBench  & & & x & x & & \\
\cline{2-8}
 & S3G2  & & x & x & x & & \\
\cline{2-8}
 & \cite{Sukthankar-SocialInfo2014}  & & & & x & & \\
\cline{2-8}
 & LDBC SNB   & & x & x & x & & \\
\cline{2-8}
  & \cite{Nettleton2016}  & & & & x & & \\
\hline
\hline   % ======================   graph analytics
\multirow{2}{*}{\rot{\textbf{An.}}}
  & HPC Scalable Graph Analysis  & & & & & x & \\
\cline{2-8}
  & Graphalytics & & & & & x & \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St.}}}
  & S2Gen & & & & & & x\\
\cline{2-8}
  & RSPLab & & & & & & x \\
%\cline{2-8}
%  & & & & & & \\
\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

\TODO{Extend summary.}
For example, some social network graph generators such as the LDBC-SNB, S3G2 or
LinkBench, can be used to test graph databases. In the case of the first two,
even though they are designed not to be specific to any type of technology,
they graph databases are their main target.  Additionally, they also provide serializers for
RDF, thus they can also be used to test RDF systems.

In the case of LinkBench, nothing prevents the user to load the generated graph
in a graph database (Facebook uses a MySQL in that paper) to
test a workload similar to Facebook and extend and complement it with more
graphy queries like those in LDBC-SNB.
